---
title: "Journal (Business Data Science Basics)"
author: "Aashik Udupi"
date: "2020-12-06"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

# Sales Analysis   
## Importing all required libraries
```{r, include=FALSE}
library(tidyverse)
library(readxl)
library(writexl)

```
## Importing Files 
```{r}
bikeshops_tbl  <- read_excel(path = "C:/Users/Aashik Udupi/Desktop/R_Projects/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")
bikes_tbl      <- read_excel(path = "C:/Users/Aashik Udupi/Desktop/R_Projects/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel(path = "C:/Users/Aashik Udupi/Desktop/R_Projects/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")
```
## Examining Data 
```{r}
bikeshops_tbl
bikes_tbl
orderlines_tbl
```
## Split Location : City, State 
```{r}
bike_shops_wrangled_tbl <- bikeshops_tbl %>%
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ",") 
bike_shops_wrangled_tbl
```
## Simplify the data 
```{r}
bikes_simplified_tbl <- bikes_tbl %>%
  select(bike.id, model, price)

orderlines_simplified_tbl <- orderlines_tbl %>%
  select(...1, order.id, order.line, customer.id, product.id, quantity)

bikeshops_simplified_tbl <- bike_shops_wrangled_tbl %>% 
  select(bikeshop.id, city, state)
bikes_orderlines_tbl <- left_join(orderlines_simplified_tbl, bikes_simplified_tbl, by = c( "product.id" = "bike.id"))

bikes_summary_tbl <- left_join(bikes_orderlines_tbl, bikeshops_simplified_tbl, by = c( "customer.id" = "bikeshop.id"))
bikes_summary_tbl
```
## Sales by State 
```{r}
sales_by_loc_tbl <- bikes_summary_tbl %>%
  select(state, price) %>%
  group_by(state) %>%
  summarize(sales = sum(price)) %>%
  mutate(Total_sales_in_Euro = scales::dollar(sales, big.mark = ".", 
                                              decimal.mark = ",", 
                                              prefix = "", 
                                              suffix = " €"))
sales_by_loc_tbl
```
## Bar Graph Plot
```{r}
sales_by_loc_tbl %>%
  ggplot(aes(x = state, y = sales)) +
  
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = Total_sales_in_Euro)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by State",
    x = "State", 
    y = "Revenue"
  )
```
## Writing Files 
```{r}
### Exporting to excel file
sales_by_loc_tbl %>%
  write_xlsx("C:/Users/Aashik Udupi/Desktop/R_Projects/00_data/01_bike_sales/02_wrangled_data/sales_by_loc_tbl.xlsx")
### Exporting to csv file
sales_by_loc_tbl %>% 
  write_csv("C:/Users/Aashik Udupi/Desktop/R_Projects/00_data/01_bike_sales/02_wrangled_data/sales_by_loc_tbl.csv")
### Exporting to rds file
sales_by_loc_tbl %>% 
  write_rds("C:/Users/Aashik Udupi/Desktop/R_Projects/00_data/01_bike_sales/02_wrangled_data/sales_by_loc_tbl.rds")
```
## Analyzing the sales by location and year (facet_wrap)
### Importing additional library
```{r, include = FALSE}
library(lubridate)
```
### Combine Data
```{r}
bike_summary_tbl <- orderlines_tbl %>%
  left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
  left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))
```
### Split Location (City & State) and Calculate Total Price 
```{r}
bike_summary_wrangled_tbl <- bike_summary_tbl %>%
separate(col = location,
         into = c("city", "state"),
         sep = ", ",
         convert = T) %>% 
mutate(total.price = price * quantity)
```
### Simplify the Table 
```{r}
bike_summary_wrangled_tbl <- bike_summary_wrangled_tbl %>%
  select(...1, order.id, order.date, customer.id, quantity, price, state, total.price)
```
### Sales by state per Year
```{r}
sales_by_year_state_tbl <- bike_summary_wrangled_tbl %>%
  select(order.date, total.price, state) %>%
  mutate(year = year(order.date)) %>%
  group_by(year, state) %>%
  summarise(sales = sum(total.price)) %>%
  ungroup() %>%
  mutate(sales_text = scales::dollar(sales, big.mark = ".",
                                     decimal.mark = ",",
                                     prefix = "",
                                     suffix = " €"))
sales_by_year_state_tbl
```
### Plotting the data
```{r}
sales_by_year_state_tbl %>%
  ggplot(aes(x = year, y = sales, fill = state)) +
  geom_col() + 
  facet_wrap(~ state) +
  geom_smooth(method = "lm", se = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".",
                                                    decimal.mark = ",",
                                                    prefix = "",
                                                    suffix = " €")) 
```
# Data Acquisition

# API
## Importing Libraries
```{r,include = FALSE}
library(tidyverse)
library(httr)
library(jsonlite)
```
## Importing data 
```{r}
fun_trivia <- GET('https://opentdb.com/api.php?amount=10')
```
### Exporting to a Tibble
```{r}
fun_trivia %>%
  .$content %>%
  rawToChar() %>%
  fromJSON() %>%
  as_tibble()
```
# Data Acquisition
## Scraping data from competitor Website
### Importing Libraries
```{r, include=FALSE}
library(tidyverse) 
library(rvest)     
library(xopen)     
library(jsonlite)  
library(glue)      
library(stringi) 
```
### Extracting Data from Rosebikes Website
```{r}
url  <- "https://www.rosebikes.de/fahrr%C3%A4der/mtb"
rose_html <- url %>% 
  read_html()
```
### Bike Names
```{r}
rose_bike_names <-  rose_html %>% 
  html_nodes(css = ".catalog-category-bikes__title-text") %>% 
  html_text() %>% 
  str_extract("(?<= ).*(?=)") %>%
  as_tibble()
rose_bike_names
```
### Bike Cost
```{r}
rose_bike_cost <-  rose_html %>% 
  html_nodes(css = ".catalog-category-bikes__price-title") %>% 
  html_text() %>% 
  str_extract("(?<= ).*(?=)") %>%
  as_tibble()
rose_bike_cost
```
### Bike Description
```{r}
rose_bike_description <-  rose_html %>% 
  html_nodes(css = ".catalog-category-bikes__subtitle") %>% 
  html_text() %>% 
  str_extract("(?<= ).*(?=)") %>%
  as_tibble()
rose_bike_description
```
### Display details in a Tabular format
```{r}
tibble(Bike_Model = rose_bike_names, Bike_cost = rose_bike_cost, Description = rose_bike_description)
```
# Data Wrangling
## Importing headers
```{r, include=FALSE}
library(tidyverse)
library(vroom)
library(data.table)
library(tictoc)
library(vroom)
```
## Importing Data
```{r}
assignee_col_types <- list(
  id = col_character(),
  type = col_integer(),
  name_first= col_skip(),
  name_last = col_skip(),
  organization = col_character()
)

assignee_tbl <- vroom(
  file       = "C:/Users/Aashik Udupi/Desktop/R_Projects/00_data/03_patent/assignee.tsv", 
  delim      = "\t", 
  col_types  = assignee_col_types,
  na         = c("", "NA", "NULL")
)

assignee_tbl
setDT(assignee_tbl)

patent_assignee_col_types <- list(
  patent_id = col_character(),
  assignee_id = col_character(),
  location_id = col_skip()
)

patent_assignee_tbl <- vroom(
  file       = "C:/Users/Aashik Udupi/Desktop/R_Projects/00_data/03_patent/patent_assignee.tsv", 
  delim      = "\t", 
  col_types  = patent_assignee_col_types,
  na         = c("", "NA", "NULL")
)

patent_assignee_tbl
setDT(patent_assignee_tbl)

tic()
patent_assignee_merged_tbl <- merge(x = patent_assignee_tbl, y = assignee_tbl, 
                                      by.x = "assignee_id", by.y = "id",
                                      all.x = TRUE, 
                                      all.y = TRUE)
toc()

patent_assignee_merged_tbl

setkey(patent_assignee_merged_tbl, "type")
key(patent_assignee_merged_tbl)
setorderv(patent_assignee_merged_tbl, c("type", "organization"))
```
## Patent Domination by Companies in USA
```{r}
patent_assignee_merge_tbl_usa <- patent_assignee_merged_tbl[ (type == 2)]
patent_assignee_merge_tbl_usa

tic()
most_patents_usa <- patent_assignee_merge_tbl_usa[!is.na(organization), .N, by = organization]
toc()
setkey(most_patents_usa, "organization")
key(most_patents_usa)
setorderv(most_patents_usa, c("N", "organization"), order = -1)
as_tibble(most_patents_usa, .rows = 10)
```
## Company with highest patent granted in 2019
```{r}
col_types_patent <- list(
  id = col_character(),
  date = col_date("%Y-%m-%d"),
  num_claims = col_integer(),
  type = col_skip(),
  number = col_skip(),
  country = col_skip(),
  abstract = col_skip(),
  kind = col_skip(),
  filename = col_skip(),
  withdrawn = col_skip(),
  title = col_skip()
)

patent_tbl <- vroom(
  file       = "C:/Users/Aashik Udupi/Desktop/R_Projects/00_data/03_patent/patent.tsv", 
  delim      = "\t", 
  col_types  = col_types_patent,
  na         = c("", "NA", "NULL")
)

setDT(patent_tbl)

tic()
patent_assignee_merge2_tbl <- merge(x = patent_assignee_merged_tbl, y = patent_tbl,
                                             by.x = "patent_id", by.y = "id",
                                             all.x = TRUE,
                                             all.y = TRUE)

toc()

patent_assignee_merge2_tbl 
```
```{r}
setkey(patent_assignee_merge2_tbl, "type")
key(patent_assignee_merge2_tbl)

setorderv(patent_assignee_merge2_tbl, c("type", "organization"))
```
```{r}
patent_assignee_merge2_tbl_usa <- patent_assignee_merge2_tbl[ (type == '2') ]

highest_patent_year <- patent_assignee_merge2_tbl_usa %>%
  select(organization, num_claims, date) %>%
  mutate(year = year(date))

highest_patent_year_2019 <- highest_patent_year[ (year == '2019') ]

setkey(highest_patent_year_2019, "organization")
key(highest_patent_year_2019)

setorderv(highest_patent_year_2019, c("num_claims", "organization"), order = -1)

task_2_ans <- highest_patent_year_2019 %>%
  select(organization, num_claims, date)

as_tibble(task_2_ans, .rows = 10)
```

## Innovation in Tech 
```{r}

col_types_uspc <- list(
  patent_id = col_character(),
  mainclass_id = col_character(),
  sequence = col_integer(),
  uuid = col_skip(),
  subclass_id = col_skip()
  
)

uspc_tbl <- vroom(
  file       = "C:/Users/Aashik Udupi/Desktop/R_Projects/00_data/03_patent/uspc.tsv",
  delim      = "\t", 
  col_types  = col_types_uspc,
  na         = c("", "NA", "NULL")
)

setDT(uspc_tbl)
uspc_tbl
```
### Most Innovative Tech Sector (by mainclass_ID)
```{r}
setkey(uspc_tbl, "mainclass_id")
key(uspc_tbl)
sorted <- uspc_tbl[,.N, by = list(mainclass_id)]
most_innovative_tech_sector <- sorted[, mainclass_id[N == max(N)]]
most_innovative_tech_sector
```
### Top 10 companies with most Patents worldwide 
```{r}
tic()
patent_assignee_merged_uspc_tbl <- merge(x = patent_assignee_merged_tbl, y = uspc_tbl,
                                           by = "patent_id",
                                           all.x = TRUE,  
                                           all.y = TRUE)
toc()

setkey(patent_assignee_merged_uspc_tbl, "type")
key(patent_assignee_merged_tbl)
?setorder()
setorderv(patent_assignee_merged_tbl, c("type", "organization"))

patent_assignee_merged_tbl_us <- patent_assignee_merged_tbl[ (type == 2)|(type == 3)]

tic()
most_patents_world <- patent_assignee_merged_tbl_us[!is.na(organization), .N, by = organization]
toc()

setkey(most_patents_world, "organization")
key(most_patents_world)
setorderv(most_patents_world, c("N", "organization"), order = -1)

as_tibble(most_patents_world, .rows = 10)
```
### Top 5 Tech Main Classes  
```{r}
setkey(patent_assignee_merged_uspc_tbl, "mainclass_id")
key(patent_assignee_merged_uspc_tbl)

?setorder()
setorderv(patent_assignee_merged_uspc_tbl, c("mainclass_id"))
patent_assignee_merged_uspc_tbl

patent_assignee_merged_uspc_tbl_world <- patent_assignee_merged_uspc_tbl[!(mainclass_id == 'na')]
patent_assignee_merged_uspc_tbl_world <- patent_assignee_merged_uspc_tbl_world[
        (organization == 'International Business Machines Corporation')|
        (organization == 'Samsung Electronics Co., Ltd.')|                                                                         (organization == 'Canon Kabushiki Kaisha')|                                                                                (organization == 'Sony Corporation')|                                                                                      (organization == 'Kabushiki Kaisha Toshiba')|                                                                              (organization == 'General Electric Company')|                                                                              (organization == 'Hitachi, Ltd.')|                                                                                         (organization == 'Intel Corporation')|                                                                                     (organization == 'Fujitsu Limited')|                                                                                       (organization == 'Hewlett-Packard Development Company, L.P.')]          

tic()
top_patent_class <- patent_assignee_merged_uspc_tbl_world[!is.na(mainclass_id), .N, by = mainclass_id]
toc()

top_patent_class

setkey(top_patent_class, "mainclass_id")
key(top_patent_class)
setorderv(top_patent_class, c("N", "mainclass_id"), order = -1)
as_tibble(top_patent_class, .rows = 5)

```
# Data Visualization
```{r, include=FALSE}
library(tidyverse)
library(vroom)
library(tictoc)
library(data.table)
library(ggplot2)
library(scales)
library(lubridate)
library(maps)
```
## Challenge : Cumulative Covid Plot
### Import Covid Data
```{r}
covid_data_tbl <- read_csv("https://opendata.ecdc.europa.eu/covid19/casedistribution/csv")
```
### Filter with countries & month
```{r}
covid_data_by_month_tbl <- covid_data_tbl %>% map_df(rev) %>%
  #select(cases, countriesAndTerritories, dateRep) %>%
  select(cases_weekly, countriesAndTerritories, dateRep) %>%
  filter(countriesAndTerritories %in% c("Germany",
                                        "United_Kingdom",
                                        "France",
                                        "Spain",
                                        "India",
                                        "United_States_of_America")) %>%
  mutate(date = dmy(dateRep)) %>% group_by( countriesAndTerritories ) %>%
  mutate(total_cases = cumsum(cases_weekly))# %>%
```
### Plot the Cumulative Cases in year 2020 
```{r}
covid_data_by_month_tbl%>%
  ggplot(aes(x = date, y = total_cases, color = countriesAndTerritories)) +
  geom_smooth(method = "gam", se = FALSE) +
  scale_color_manual(values=c("#000000", "#ff0016", "#3ea6d7", "#feff00", "#106a00", "#ff8e02"))+
  labs(title = "Confirmed covid cases worldwide",
       x = "Year 2020",
       y = "Cases")
```
### Challenge : Visualize distribution of mortality rate
```{r}
world <- map_data("world")

covid_by_mortality_tbl <- covid_data_tbl %>%
  mutate(across(countriesAndTerritories, str_replace_all, "_", " ")) %>%
  mutate(countriesAndTerritories = case_when(
    
    countriesAndTerritories == "United Kingdom" ~ "UK",
    countriesAndTerritories == "United States of America" ~ "USA",
    countriesAndTerritories == "Czechia" ~ "Czech Republic",
    TRUE ~ countriesAndTerritories
    
  ))%>%
  #group_by(countriesAndTerritories, popData2019, deaths) %>%
  group_by(countriesAndTerritories, popData2019, deaths_weekly) %>%
  summarise(total_pop = max(popData2019))%>%
  #summarise(total_death = sum(deaths))%>%
  summarise(total_death = sum(deaths_weekly))%>%
  summarise(mortality =  (total_death)/(popData2019))

class(covid_by_mortality_tbl)
setDT(covid_by_mortality_tbl)
class(covid_by_mortality_tbl)
covid_by_mortality_tbl %>% glimpse()
setDT(world)
world %>% glimpse()

tic()
covid_by_map_tbl <- merge(x = world, y = covid_by_mortality_tbl, 
                          by.x = "region", by.y = "countriesAndTerritories",
                          all.x = TRUE, 
                          all.y = FALSE)

toc()
covid_by_map_tbl%>% glimpse()

setkey(covid_by_map_tbl, "region")
key(covid_by_map_tbl)

setorderv(covid_by_map_tbl, c("mortality", "region", "long", "lat"), order = -1)

covid_by_map_tbl%>%
  ggplot() +
  geom_map(aes(x = long, y = lat, map_id = region, fill = mortality),map = world) +
  scale_fill_continuous(labels = scales::percent, low = "white", high="red")+
  labs(title = "Confirmed Covid19 deaths relative to size of the population ",
       subtitle = "More than 1.83 Million confirmed covid19 deaths worldwide")
```


